### 2016-11-17 README.Rmd
Add travis
Turn off Travis badge for the moment
Update README

@@

Once you've loaded the dataframe, you can load the included data using the `data` function. For example:

@@

The following datasets are included with the package:

- `closest_dist`
- `county_centers`
- `hurr_tracks`
- `rain`

For each, you can see the helpfiles for the data for more information about the data included in each.

>>>>

```{r eval = FALSE, echo = FALSE}
[![Travis-CI Build Status](https://travis-ci.org/geanders/hurricaneexposure.svg?branch=master)](https://travis-ci.org/geanders/hurricaneexposure)
```

@@

The following datasets are included with the `hurricaneexposuredata` package:

- `closest_dist`: A dataframe that gives the distance and date-time for the closest approach of each tropical storm to the mean population center of each US county in states in the eastern half of the United States.
- `county_centers`: A dataset containing the latitude and longitude of the center of population of every United State county, based on population as of the 2010 US Census.
- `hurr_tracks`: A dataset containing the storm tracks for Atlantic basin tropical storms between 1988 and 2012, from the Extended Best Track Dataset for the Atlantic basin.
- `rain`: A dataframe that gives the total rainfall in US counties for a one-week window centered at the date on which the tropical storm was closest to the county for Atlantic basin storms between 1988 and 2011.
- `storm_winds`: A dataframe that gives modeled windspeeds in US counties for all eastern US counties for Atlantic basin tropical storms between 1988 and 2011.
- `storm_events`: A dataframe that gives county-specific severe storm events listed in US counties temporally and spatially close to storm tracks for all eastern US counties for Atlantic basin tropical storms between 1988 and 2011.

Once you've loaded the `hurricaneexposuredata` package, you can load the included data using the `data` function. For example:

@@

For each dataset, you can see the helpfiles for the data for more information. For example:

```{r eval = FALSE}
?hurr_tracks
```
